---
title: "p8105_hw1_RUOYING"
author: "RUOYING DENG"
date: "2023-09-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Since my computer is HUAWEI, I need to manually change the system language into English
Sys.setlocale("LC_ALL", "English")
```

```{r}
usethis::use_git_config(user.name ="rd3097", user.email = "rd3097@cumc.columbica.edu")
library("tidyverse")
library("moderndive")
```
## Problem 1
```{r}
data("early_january_weather")
skimr::skim(early_january_weather)
```
The variable names included in this datasets are `r colnames(early_january_weather)`.

The size of the data sets is that it has `r nrow(early_january_weather)` rows.

The number of columns is `r ncol(early_january_weather)`.

The mean temperature of early january weather is `r mean(early_january_weather$temp)` degrees.

```{r}
ggplot(early_january_weather,aes(x = time_hour, y = temp, color = humid)) + geom_point()
```
This graph shows that the temperature tends to become higher during early January, and achieves its highest peak at January 14th. The temperature also vibrate a lot each day. The humidity acheives its highest before January 14th.

```{r}
ggsave("weather_scatterplot.pdf")
```

#Problem 2
```{r}
# create the dataframes
df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = c(vec_numeric > 0),
  vec_char = c("Red", "Yellow", "Green", "Red", "Red", "Yellow", "Red", "Green", "Green", "Yellow"),
  vec_factor = factor(vec_char, level=c("Red", "Yellow", "Green"))
)  


#calculate the mean value of each variable

numeric = pull(df,vec_numeric)
logical = pull(df, vec_logical)
char = pull(df, vec_char)
factor = pull(df, vec_factor)

```
The mean of a random sample of size 10 from a standard Normal distribution is `r mean(numeric)`.
The mean of a logical vector indicating whether elements of the sample are greater than 0 is `r mean(logical)`.
The mean of a character vector of length 10 is `r mean(char)`.
The mean of a factor vector of length 10, with 3 different factor “levels” is `r mean(factor)`.

The mean works for numeric and logical variables, but it doesn't work for character and factor variables.

```{r}
# convert logical, character, and factor variables to be numerical
numeric_logical = as.numeric(logical)
numeric_character = as.numeric(char)
numeric_factor = as.numeric(factor)
```

Logical variable can be convert to numerical variable, where TRUE convert to 1, and FALSE convert to 0. So the mean can be calculated as `r mean(numeric_logical)`. Factor vector will be assigned a numeric value to each factor level based on the order of appearance.The mean of factor variable is `r mean(numeric_factor)`.
For character variable, it contains non-numeric characters, so it cannot be convert to numerical variable, then the mean cannot be calculated.The output of mean is `r mean(numeric_character)`
