---
title: "p8105_hw1_RUOYING"
author: "RUOYING DENG"
date: "2023-09-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
usethis::use_git_config(user.name ="rd3097", user.email = "rd3097@cumc.columbica.edu")
library("tidyverse")
library("moderndive")
```
## Problem 1
```{r}
data("early_january_weather")
skimr::skim(early_january_weather)
```
The variable names included in this datasets are `r colnames(early_january_weather)`.

The size of the data sets is that it has `r nrow(early_january_weather)` rows.

The number of columns is `r ncol(early_january_weather)`.

The mean temperature of early january weather is `r mean(early_january_weather$temp)`degrees.

```{r}
ggplot(early_january_weather,aes(x = time_hour, y = temp, color = humid)) + geom_point()
```
> This graph shows that the temperature tends to become higher during early January, and achieves its highest peak at January 14th. The temperature also vibrate a lot each day. The humidity acheives its highest before January 14th.

```{r}
ggsave("weather_scatterplot.pdf")
```

#Problem 2
```{r}

df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = c(vec_numeric > 0),
  vec_char = c("Red", "Yellow", "Green", "Red", "Red", "Yellow", "Red", "Green", "Green", "Yellow"),
  vec_factor <- factor(vec_char, levels =c("Level1", "Level2", "Level3"))
)
print(df)
```
